Machine learning guided batched design\\ of a bacterial Ribosome Binding Site

### 2022-01-05 paper/methods.tex
cheng's changes in intro
Swapped final paragraphs.

%! TEX root=./main.tex
\section{Methods}

@@

To find RBS sequences with the highest possible TIR score after a total number of rounds $N$, we consider our experimental design problem as a sequential optimisation of an unknown reward function $f: \mathcal{D} \rightarrow \mathbb{R}$, where $\mathcal{D}$ is the set containing all RBS sequence points in the design space, and $f(\mathbf{x})$ is the TIR score of the 6-base core sequence \hl{ of the RBS} $\mathbf{x} \in \{A,C,G,T\}^{6}$.
In each Round $t$, we choose a set of $m$ points $\mathcal{S}_t \subset \mathcal{D}$ and observe the function value at each point in the selected set $\mathcal{S}_t$, i.e. $y_i = f(\mathbf{x}_i) + \epsilon$, for all $i \in \mathcal{S}_t$, where $\epsilon$ is the Gaussian random noise with unknown mean and \hl{standard deviation}. \\
% This noise is influenced by the accuracy of the RBS predictor and other experimental sources of interference (e.g. time, temperature, operator, etc.). 
% REVIEW:
% \mengyan{we should discuss measurement noise somewhere, maybe with a sample example for the dataset we used.}

>>>>

%! TEX root=./main.tex
\section{Materials and Methods}

@@

To find RBS sequences with the highest possible TIR score after a total number of rounds $N$, we consider our experimental design problem as a sequential optimisation of an unknown reward function $f: \mathcal{D} \rightarrow \mathbb{R}$, where $\mathcal{D}$ is the set containing all RBS sequence points in the design space, and $f(\mathbf{x})$ is the TIR score of the 6-base core sequence of the RBS $\mathbf{x} \in \{A,C,G,T\}^{6}$.
In each Round $t$, we choose a set of $m$ points $\mathcal{S}_t \subset \mathcal{D}$ and observe the function value at each point in the selected set $\mathcal{S}_t$, i.e. $y_i = f(\mathbf{x}_i) + \epsilon$, for all $i \in \mathcal{S}_t$, where $\epsilon$ is the Gaussian random noise with unknown mean and standard deviation. \\
% This noise is influenced by the accuracy of the RBS predictor and other experimental sources of interference (e.g. time, temperature, operator, etc.). 
% REVIEW:
% \mengyan{we should discuss measurement noise somewhere, maybe with a sample example for the dataset we used.}
